Balsa: A Compact Line Notation Based on SMILES

### 2022-09-11 manuscript.tex
Describes a fix for atifactual double bond conformations. Closes #51

An error must be reported should any of these states be encountered. Note that it is possible for a conformation to be both overspecified on one side and underspecified on the other.

@@

@@

Cyclic conjugated polyenes present special challenges to the use of PPBs, as exemplified by cyclooctatetraene (Figure~\ref{fig:cyclooctatetraene}). Although the (\textit{syn}, \textit{syn}, \textit{syn}, \textit{syn}) conformation is expressable, the (\textit{syn}, \textit{syn}, \textit{syn}, \textit{anti}) conformation is not. This problem arises because the conformation for two different double bonds is set by the same PPB.

>>>>

An error must be reported should any of these states be encountered. Note that it is possible for a conformation to be both overspecified on one side of a double bond and underspecified on the other.

@@

A different kind of problem arises in the case of 2,4,6-octatriene, where the conformations of both outer double bonds are set but the conformation of the interior double bond is unknown (Figure~\ref{fig:artifactual-bond-conformation}) \cite{mayfield:2022}. The use of PPBs along carbon-carbon bonds artifactually sets the inner double bond conformation. In this case the problem can be solved by reifying the hydrogens attached to the interior double bond, then directing PPBs along the resulting carbon-hydrogen bonds. This is, however, not a general solution. It will fail, for example, in the case of a nitrogen-nitrogen bond due to the lack of reifiable hydrogens.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{artifactual-bond-conformation.pdf}
    \caption{Artifactual bond conformation. Placing PPBs along carbon-carbon bonds sets the interior double bond's conformation artifactually to \textit{anti} (left). This problem can be addressed by hydrogen reification followed by partial parity assignment to the newly-available carbon-hydrogen bonds (right).}
    \label{fig:artifactual-bond-conformation}
\end{figure}

@@

Cyclic conjugated polyenes present special challenges to the use of PPBs, as exemplified by cyclooctatetraene (Figure~\ref{fig:cyclooctatetraene}). Although the (\textit{syn}, \textit{syn}, \textit{syn}, \textit{syn}) conformation is expressable using PPBs located along carbon-carbon axes only, the (\textit{syn}, \textit{syn}, \textit{syn}, \textit{anti}) conformation is not. This problem arises because the conformation for two different double bonds is set by the same PPB.
